A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-11-29 writeup/revision 1/paper.tex
significance in table 3
Moving table around

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
\centering
\scriptsize
\begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
\hline
workers & quality & speed & \\\hline
%many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
%&&slow& ar ga he pa sv tr\\\cline{2-4}
%& low or medium &fast& hi mr ta ur \\\cline{3-4}
%&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5}   Dutch, French, German, Gujarati, Italian, Kannada, Malayalam, Portuguese, Romanian, Serbian, Spanish, Tagalog, Telugu \\\cline{3-4}
&&slow& Arabic,  Hebrew, Irish, Punjabi, Swedish, Turkish\\\cline{2-4}
& low or  &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
&medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, Ukranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
&low or  &fast&--\\\cline{3-4}
&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}  Esperanto, Ido, Kurdish, Persian, Quechua, Wolof, Zazaki\\\hline
\end{tabular}
\caption{The green box shows the languages which we have found most supported by MTurk in terms of worker population, worker ability, and speed of completion. Languages have ``many'' workers if we recorded more than 50 active in-region Turkers. Languages are ``high'' quality if they average greater than 70\% accuracy on our controls. Languages are ``fast'' if all of our translations (approx. 10,000 words each) were completed within two weeks.}
\label{recommendations}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

With the publication of this paper, we are releasing all data and code used in this study.  Our data release includes the raw data, along with bilingual dictionaries that are filtered to be high quality. It will include 256,604 translation assignments from 5,281 Turkers and 20,952 synonym assignments from 1,005 Turkers, along with meta information like geolocation and time submitted, plus external dictionaries used for validation. The dictionaries will contain 1.5M total translated words in 100 languages, along with code to filter the dictionaries based on different criteria.  The data also includes parallel corpora for six Indian languages, ranging in size between 700,000 to 1.5 million words

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\centering
\small
\footnotesize
\begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
\hline
\footnotesize workers & \footnotesize  quality & \footnotesize speed & \\\hline
%many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
%&&slow& ar ga he pa sv tr\\\cline{2-4}
%& low or medium &fast& hi mr ta ur \\\cline{3-4}
%&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5}    Dutch, French, German, Gujarati, Italian, Kannada, Malayalam, Portuguese, Romanian, Serbian, Spanish, Tagalog, Telugu \\\cline{3-4}
&&slow& Arabic,  Hebrew, Irish, Punjabi, Swedish, Turkish\\\cline{2-4}
& low or  &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
&medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, Ukranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
&low or  &fast&--\\\cline{3-4}
&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}  Esperanto, Ido, Kurdish, Persian, Quechua, Wolof, Zazaki\\\hline
\end{tabular}
\normalsize
\caption{The green box shows the best languages to target on MTurk. These languages have many workers who generate high quality results quickly. We defined {\it many} workers as 50 or more active in-region workers, {\it high} quality as $\geq$70\% accuracy on the gold standard controls, and {\it fast} if all of the 10,000 words were completed within two weeks.}
\label{recommendations}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

With the publication of this paper, we are releasing all data and code used in this study.  Our data release includes the raw data, along with bilingual dictionaries that are filtered to be high quality. It will include 256,604 translation assignments from 5,281 Turkers and 20,952 synonym assignments from 1,005 Turkers, along with meta information like geolocation and time submitted, plus external dictionaries used for validation. The dictionaries will contain 1.5M total translated words in 100 languages, along with code to filter the dictionaries based on different criteria.  The data also includes parallel corpora for six Indian languages, ranging in size between 700,000 to 1.5 million words.
